\begin{rubric}{Experience}

\entry*[2023 -- Present]%
    \textbf{Co-Chair, "Nena Aruna" Project}, Rotaract Club of University of Moratuwa
    \par Coordinated educational initiatives aimed at guiding O/L students through exam preparation and post-exam planning.
    \par Developed and implemented strategic plans for academic support programs.

\entry*[2023 -- Present]%
    \textbf{HRM Member}, MoraSpirit, University of Moratuwa
    \par Active member of the Human Resources Management pillar.
    \par Contributed to InterUni coverage and 14th anniversary celebration.
    \par Participated in Outside Recruitment projects.

\entry*[2023]%
    \textbf{District Coordinator, "Ganitha Sawiya" Project}, Sasnaka Sansada
    \par Managed mathematics teaching program for O/L students in Galle district.
    \par Coordinated volunteer teachers and scheduled classes.
    \par Monitored student progress and implemented improvement strategies.

\entry*[2022 -- 2023]%
    \textbf{Co-chair, "Regreen Earth Madol Duwa" Project}, Sasnaka Sansada
    \par Led mangrove reforestation project.
    \par Coordinated volunteers and resources for environmental conservation.

\entry*[2022 -- 2023]%
    \textbf{Volunteer Teacher}, Sasnaka Sansada
    \par Taught subjects to underprivileged students.
    \par Participated in charity projects including "Katina Pinkama".
    \par Contributed to blood donation programs.

\entry*[2023 -- Present]%
    \textbf{District Coordinator, "Shilpasara" Project}, LEO Club of University of Moratuwa
    \par Initially volunteered as a teacher in the educational initiative.
    \par Promoted to district coordinator, overseeing project implementation.
    \par Provided guidance to O/L students both pre and post examination.

\end{rubric}